### 2024-09-12 cognitive-bias.qmd
20240912 - add to bulleted list

- [base rate fallacy](#sec-fallaciesBaseRate) (aka base rate neglect)
- [regression fallacy](#sec-fallaciesRegression)
- [hot hand fallacy](#sec-fallaciesHotHand)
- [sunk cost fallacy](#sec-fallaciesSunkCost)
- [gambler's fallacy](#sec-fallaciesGambler)
- [anecdotal fallacy](#sec-fallaciesAnecdotal)
- [conditional probability fallacy](#sec-fallaciesConditionalProbability)
- [ecological fallacy](#sec-fallaciesEcological)

>>>>

- [base rate fallacy](#sec-fallaciesBaseRate) (aka base rate neglect)
- [regression fallacy](#sec-fallaciesRegression)
- [hot hand fallacy](#sec-fallaciesHotHand)
- [sunk cost fallacy](#sec-fallaciesSunkCost)
- [gambler's fallacy](#sec-fallaciesGambler)
- [anecdotal fallacy](#sec-fallaciesAnecdotal)
- [narrative fallacy](#sec-fallaciesNarrative)
- [conditional probability fallacy](#sec-fallaciesConditionalProbability)
- [ecological fallacy](#sec-fallaciesEcological)
